Unit tests

### 2018-03-14 Tests.Rmd
added a new surrogate routine and tests for it

# Test flexible copula functions
We here test the functions `Corbds`, `Pbds` and `D2bds`.

@@

# Tests to model selection tool

>>>>

# Test flexible copula tail dependency statistics
We here test the functions `Corbds`, `Pbds` and `D2bds`.

@@

Test the `copsurrognd` function:
```{r test_copsurrognd, echo=T, cache=T, cache.extra=list(mtime("copsurrognd.R"))}
library("VineCopula")
source("copsurrognd.R")
set.seed(101)

#basic tests
datcop<-claytonCopula(3,dim=3)
numpts<-1000
m<-rCopula(numpts,datcop)
plot(m[,1],m[,2],type='p',asp=1)
rect(0,0,1,1)
plot(m[,1],m[,3],type='p',asp=1)
rect(0,0,1,1)
plot(m[,2],m[,3],type='p',asp=1)
rect(0,0,1,1)

tarcop<-gumbelCopula(8,dim=3)

res<-copsurrognd(m=m,targetcop=tarcop,numsurrog=5)
if (sum(dim(res)[1:2]==dim(m))==2)
{
  print("passed")
} else
{
  print("dim of output is wrong")
}

cor(res[,1,1],res[,2,1],method="kendall")
cor(res[,1,1],res[,3,1],method="kendall")
cor(res[,2,1],res[,3,1],method="kendall") #these should be similar to each other and to the following...

gd<-rCopula(1000,tarcop)
cor(gd[,1],gd[,2],method="kendall")
cor(gd[,1],gd[,3],method="kendall")
cor(gd[,2],gd[,3],method="kendall")

#but not to these, because correlations match the target, not the original data
cor(m[,1],m[,2],method='kendall')  
cor(m[,1],m[,3],method='kendall')  
cor(m[,2],m[,3],method='kendall')

plot(res[,1,1],res[,2,1],type='p',asp=1) #should look like a Gumbel
rect(0,0,1,1)
plot(res[,1,1],res[,3,1],type='p',asp=1) #should look like a Gumbel
rect(0,0,1,1)
plot(res[,2,1],res[,3,1],type='p',asp=1) #should look like a Gumbel
rect(0,0,1,1)
BiCopGofTest(res[,1,1],res[,2,1],family=4) #should indicate an acceptable fit; 
                                            #family=4 is Gumbel
BiCopGofTest(res[,1,1],res[,3,1],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,2,1],res[,3,1],family=4) #should indicate an acceptable fit

if (sum(sort(res[,1,1])==sort(m[,1]))==numpts &&
    sum(sort(res[,2,1])==sort(m[,2]))==numpts &&
    sum(sort(res[,3,1])==sort(m[,3]))==numpts &&
    sum(sort(res[,1,2])==sort(m[,1]))==numpts &&
    sum(sort(res[,2,2])==sort(m[,2]))==numpts &&
    sum(sort(res[,3,2])==sort(m[,3]))==numpts)
{
  print("passed")
} else
{
  print("Columns of output of copsurrog should be permutations of the corresponding 
        columns of the input")
}
```

# Tests of model selection tool
